Species turnover reveals hidden effects of decreasing Nitrogen deposition in mountain hay meadows

### 2018-06-29 Manuscript.Rmd
Update Manuscript.Rmd

While we could not detect a consistent decrease in average indicator values for nutrients (Table \@ref(tab:communitytrendstab)), the higher colonization rate of species with low nutrient value at sites with low deposition rate seems to affect the spatial variation of oligotrophic species richness: sites with low Nitrogen deposition are likely to become more species rich over time likely resulting in steeper slope of the negative relationship between Nitrogen deposition and oligotrophic species richness. Indeed, if we apply a similar model as in @Roth2013 at different points in time to infer the effects of Nitrogen deposition on the spatial variation of oligotrophic species richness, the resulting effect size (i.e. the slope) became more negative over time (Fig. \@ref(fig:figconsequences)).

>>>>

While we could not detect a consistent decrease in average indicator values for nutrients (Table \@ref(tab:communitytrendstab)), the higher colonization rate of species with low nutrient value at sites with low deposition rate seems to affect the spatial pattern of oligotrophic species richness: sites with low Nitrogen deposition are likely to become more species rich over time likely resulting in steeper slope of the negative relationship between Nitrogen deposition and oligotrophic species richness. Indeed, if we apply a similar model as in @Roth2013 at different points in time to infer the effects of Nitrogen deposition on the spatial variation of oligotrophic species richness, the resulting effect size (i.e. the slope) became more negative over time (Fig. \@ref(fig:figconsequences)).
